Robust and Efficient CSI Compression Using CLLWCsiNet in Noisy MIMO Environments

### 2025-04-06 paper_latex_edit - Copy.tex
✅ Citation-rich Deep Learning for CSI Feedback: One-Sided Model and Joint Multi-Module Learning Perspectives

@@

>>>>

\cite{Guo2024} addresses two critical challenges in DL-based CSI feedback: vendor coordination overhead and modular design inefficiencies. The authors propose a \textit{one-sided} CSI-PPPNet architecture requiring only 4.3\% of conventional model parameters (175K vs. 4095K), while supporting variable compression ratios without retraining. Their joint multi-module learning framework demonstrates a 15--20\% spectral efficiency improvement over decoupled approaches by simultaneously optimizing CSI feedback, channel coding, and precoding modules.

@@

	\bibitem{Guo2024} 
	Y. Guo, W. Chen, F. Sun, J. Cheng, M. Matthaiou, and B. Ai, 
	``Deep Learning for CSI Feedback: One-Sided Model and Joint Multi-Module Learning Perspectives,'' 
	\textit{arXiv preprint arXiv:2405.05522}, 
	2024.
